Storm Surges

### 2014-07-15 RoughWork/manuscript.tex
Tried making a nicer bathy image.
New bathymetry and domain image
Included no_pressure run in analysis, but didn't save the figure.

\documentclass[pdftex,10pt]{article}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{epspdfconversion}

@@

\begin{figure}[h]
\centering
\includegraphics[scale=0.5]{Figures/bathy.png}
\caption{Model domain including bathymetry, rivers (*), and storm surge locations (o) of interest.}\label{fig:domain}
\end{figure}
%image needs some work: colour? labels for JdF, SoG, cities...

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/feb2006_factors.pdf}
\caption{Comparison of the modelled residual for three simulations: A simulation with all forcing (blue), a simulation without atmospheric forcing (green), and a simulation without the sea surface height anomaly. }
\label{fig:factors}
\end{figure}
%not sure about the colours, but different line styles is really hard to make out.

>>>>

\documentclass[pdftex,10pt]{article}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amsmath}

@@

\begin{figure}[h]
\centering
\includegraphics[scale=0.5]{Figures/bathy.pdf}
\caption{Model domain (highlighted area) including bathymetry, rivers (blue circles), and storm surge locations of interest  (red stars).}\label{fig:domain}
\end{figure}
%image needs some work: colour? labels for JdF, SoG, cities...

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{Figures/feb2006_factors.pdf}
\caption{Comparison of the modelled residual for three simulations: A simulation with all forcing (blue), a simulation without atmospheric forcing (green), and a simulation without the sea surface height anomaly (red). }
\label{fig:factors}
\end{figure}
%not sure about the colours, but different line styles is really hard to make out.
